Flatiron cleaning

### 2022-04-06 Rmd/Serous Adjusted weight rdi analysis.Rmd
Add Rmd for limited analysis on serous histology OC + fix carbo only analysis

# `r emo::ji("spiral_notepad")` This report is using **actual weight** in OC with **SEROUS** histology.

@@

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

@@

<!-- **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.   -->

@@

```{r plot interval}
# Treatment %>% 
#   ggplot(aes(x= interval_creat)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# # Treatment %>% 
# #   ggplot(aes(x= interval_height)) +
# #   geom_bar() +
# #   coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_weight)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_bsa)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_auc)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
```

@@

- include patients whose histology of SEROUS CANCER    
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) %>% 
  filter(histology == "Serous")

@@

# Consort diagram

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(histology == "Serous") %>% 
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

    Frontline = standard_care,

  # anti_join is useful for counting exclusions -------------
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • (Data from one PracticeID) <br>
      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include only patients who received platin and/or taxane <br>
      • exclude patients who only received neo + surgery <br>
      • include patients with single or dual P/T +/- Bev as frontline treatment
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

  consort_arrow_add(
    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
  ) %>%
  consort_arrow_add(
    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```

@@

Left is univariable, right is adjusted by each drugs `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,` but not by clinicals.

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
`imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
`imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
`raceeth + ageatdx + imp_stagecat + imp_debulking` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

>>>>

# `r emo::ji("spiral_notepad")` This report is using **adjusted weight** in OC with **SEROUS** histology.

@@

IF actual_bmi < 25 :
$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
IF actual_bmi >= 25 :

$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
In both cases CrCl is capped at 125.  
<br>

@@

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.

@@

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) %>% 
  filter(histology == "Serous")

@@

@@

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +`
`raceeth + ageatdx + imp_stagecat + imp_debulking` 
```{r Table 5 HR adjusted rdi group}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + `
`raceeth + ageatdx + imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
`raceeth + ageatdx + imp_stagecat + imp_debulking` 
```{r rdi continous}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
`raceeth + ageatdx + imp_stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
`raceeth + ageatdx + imp_stagecat + imp_debulking` 
```{r rdi continous adjusted by other drug}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

@@

`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~`
`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
`raceeth + ageatdx + stagecat` 
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl2, tbl3),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>
